---
title: "Assignment 2: Survey developpment"
subtitle: "105.708 Data Acquisition and Survey Methods"
author: "Group 3: Gjorgieva Aleksandra(), de Lambertye Grégoire(12202211),	Loos Annika Katharina()"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
suppressMessages(library(dplyr))
suppressMessages(library('xml2'))
suppressMessages(library(rvest))
suppressMessages(library(tidyverse))
suppressMessages(library(httr))
suppressMessages(library(janitor))
suppressMessages(library(lubridate))
```

# 1. Introducction 

## 1.1 topic

blabla -> Alexandra

## 1.2 Hypothesis 

blabla -> Alexandra

## 1.3 question 

blaba -> Alexandra

# 1.4 Data exploration 

```{r}
file_path <- "./data/group_3.csv"

rawData <- read.csv(file_path, sep=";")
# rename the column in a english friendly format 
colnames(rawData)[4] <- "answer_1" 
colnames(rawData)[5] <- "answer_2" 
colnames(rawData)[6] <- "answer_3"

print(head(rawData))
print(paste("The data set dimensions are ", dim(rawData)[1], " x ", dim(rawData)[2]))
```

## 1.5 Preprocessing 

The colummns Gender and Age look nice and don't requier preprocessing.  

```{r}
print(unique(rawData[3]))
```

As we see the format differs for the academic program answer. Where we have missing information we associate them by default to Data Science / MSc / TU Wien. To say we change "Data Science", "MSc Data Science", "MSc", "Data Science Msc", "	Data Science MSc." to "Data Science / MSc / TU Wien". 

```{r}
row_index <- which(rawData$Academic.Program %in% c("Data Science", 
                                                   "Data Science / MSc / TU Wien", 
                                                   "MSc Data Science", 
                                                   "Data Science / MSc / TU WIen",
                                                   "MSc", 
                                                   "Data Science Msc", 
                                                   "Data Science MSc."))

rawData[row_index, "Academic.Program"] <- "Data Science / MSc / TU Wien"
```


```{r}

print(unique(rawData[3]))
```

```{r}
rawData$answer_2 <- str_sub(rawData$answer_2, end = 2)
rawData$answer_2 <- as.numeric(rawData$answer_2)
```


```{r}
for (i in 1:length(rawData$answer_1)){
  if(rawData$answer_1[i] <= 5){
    rawData$answer_1[i] <- rawData$answer_1[i] * 60
  }
}
```



```{r}
head(rawData)
```
 

## 2. hypothesis 1 -> Alexandra

# 3. Hypothesis 2: "Student that identify themself as female are more prone to consume longer video content than others."

## 3.1 Exploratory Data Analysis

For the categorical features in the data set, one can use charts to visualize the distribution of each category. 

## 3.1.1 Distribution of Gender

In our study there where 22 males and 16 females taking part, shown in a bar and a pie chart.

```{r}
ggplot(rawData, aes(x = Gender, fill = Gender)) +
  geom_bar(show.legend = TRUE) +
  theme(axis.text.x = element_blank()) +
  labs(x = "Gender", y = "Count") + 
  ggtitle("Distribution of Genders") +
  theme(plot.title = element_text(hjust = 0.5, vjust = -0.3)) +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5)
```

```{r}
ggplot(rawData, aes(x = "", fill = Gender)) +
  geom_bar(width = 1) +
  coord_polar(theta = "y") +
  labs(x = NULL, y = NULL, fill = "Gender") +
  ggtitle("Distribution of Genders") +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5, vjust = -0.3)) + 
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -7)
```

## 3.1.2 Distribution of type of Video Content

The third question of our study was "From what category do you consume the most video content from?", where the participants could choose between five categorical values: "Movies","TV shows (series)", "YouTube shorts – Tiktoks – Intsagram reels", "Youtube videos" or "None of them". In the following bar chart one can visually see the distriubtion between the five values with "Youtube Video" beeing the most popular category, because it was chosen 20 times. On the other hand only one person watches mainly movies.

```{r}
ggplot(rawData, aes(x = answer_3, fill = answer_3)) +
  geom_bar(show.legend = TRUE) +
  labs(x = "Video Content Type", y = "Count") +
  theme(axis.text.x = element_blank()) +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5) +
  ggtitle("Distribution of Video Content Categories") +
  theme(plot.title = element_text(hjust = 3, vjust = 1))
```

## 3.2 Descriptive Inference:

## 3.2.1 Average watching time

In general one can see by this table that females taking part in our study in average watch less video content than male participants.

```{r}
summary_stats <- rawData %>%
  group_by(Gender) %>%
  summarize(average_duration = mean(answer_1),
            median_duration = median(answer_1))

summary_table <- data.frame(Gender = summary_stats$Gender,
                            Average_Duration = summary_stats$average_duration,
                            Median_Duration = summary_stats$median_duration)

summary_table
```

```{r}
rawData[, "Gender"] <- ifelse(rawData[, "Gender"]=="male",1,0)
rawData$answer_3 <- factor(rawData$answer_3, levels = c( "Movies", "None of them", "TV shows (series)","YouTube shorts – Tiktoks – Intsagram reels", "YouTube video"))
rawData$answer_3 <- as.integer(rawData$answer_3)
rawData$Gender <- as.numeric(rawData$Gender)
rawData
```

## 3.2.1 Distribution of Video Content Categories for each Gender

In the following chart one can see that males watch more video content of the category "YouTube video" than females. The rest is fairly balanced.

```{r}
Genders <- factor(rawData$Gender, labels = c("female", "male"))

ggplot(rawData, aes(x=factor(answer_3),fill = Genders)) +
  geom_bar(position = "dodge") +
  labs(x = "Video Content Type", y = "Count") +
  ggtitle("Distribution of Video Content Categories for each Gender") +
  theme(plot.title = element_text(hjust = 0.5, vjust = -0.3)) +
  scale_x_discrete(labels = c("Movies", "None", "TV shows", "Reels / Shorts", "YouTube video"))
```


## 3.3 Analytic Inference::

```{r}
contingency_table <- table(rawData$Gender, rawData$answer_3)
contingency_table

chi_squared_test <- chisq.test(contingency_table)
chi_squared_test
```

The p-value is a measure of the statistical significance of the association. In this case, the p-value is 0.003273. A p-value less than the chosen significance level (e.g., 0.05) indicates that the association between gender and the categorical value in the fifth column is statistically significant. One can see that more males watch Youtube Videos which can be put into a category of longer content and more females watch video content of the category "YouTube shorts – Tiktoks – Intsagram reels". Therefore the hypothesis of "Student that identify themself as female are more prone to consume longer video content than others" can be rejected.

# 3 Hypothesis 3

The 3rd hypothesis was *- Students think they spend too much time watching video content, regardless on the time they spend doing it.*. In other word, we are looking for the correlation between the time spend watching video and the answered provided for the question 2. Let's have first a deeper look to those columns. The following table show the answer repartition. 

```{r, out.width="50%"}
pie( table(rawData$answer_2),
    main = "Distribution of answers for question 2",
    col = c("#ff0000", "#ffa700", "#fff400", "#a3ff00", "#2cba00"),
    labels = paste0(names(table(rawData$answer_2)), ": ", table(rawData$answer_2)))

legend("topright",
       legend = names(table(rawData$answer_2)),
       fill = c("#ff0000", "#ffa700", "#fff400", "#a3ff00", "#2cba00"),
       cex = 0.8,
       title = "Answers")
```

A majority of the answers are between 4 and 5 (66%). This let us think that people have a generaly a bad opinion on the time they spend watching video content.  But how is it correlated to the real time they spend?  

```{r}
correlation <- cor(rawData$answer_1, rawData$answer_2)
print(paste('The correlation is ', correlation))
```

The correlation between the 2 column is 0.38, a strong correlation is close to 1 and a correlation between 0.3 and 0.5 is generally considered as low. 

So far we saw that a majority of the people think they spend too much time watching video content and this is weakly correlated to the real time. We could accept our hyothis but the indicators are not straightforward. A more visual approach is to look at the distribution of the time regarding the "look at themself". This have been done in the following graph. 

```{r, out.width="80%"}
plot <- ggplot(rawData, aes(x = answer_1, fill = as.factor(answer_2))) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = 
                      c("#ff0000", "#ffa700", "#fff400", "#a3ff00", "#2cba00")) + 
  labs(fill = "answer_2") +
  xlab("Time spended watching video (in min)") +
  ggtitle("Density of the time spended watching video per look at themselves")

plot
```
On this graph we can see that the density for answer 1 ("I don't think I spend too much time") has 2 spikes, one small (time < 50 min) and one around 200 mins. For the opposite answer (5, I think I should spend less time watching video content) we have a spike around 120 minutes and a second one around time > 320 minutes. For the other distribution they are pretty similar and centered around 120 minutes. We have to take in account that some densities are computed on very few data (as for answer 3 where only 3 peoples selected this answer).

If our hypothesis were exact we should only have people with answer 4 or 5 and the same densities for the answers. But here we clearly see that when people watch video less than 30 min per day they have a good opinion on it (1 or 2). On the opposite every person that watch video more than 300 minutes per day think he/she should watch less video. So **we reject our third hypothesis**.  

Diving a bit deeper in the analysis made us consider the values without the "outliers", to say without the values under 30 minutes (5 peoples) and more than 300 minutes a day (2 peoples). We recomputed the correlation and redraw the previous plot. 

```{r, echo = FALSE, figures-side, fig.show="hold", out.width="50%"}
data <- rawData %>%
  filter(answer_1 > 30 & answer_1 < 300)

pie(table(data$answer_2),
    main = "Distribution of answers for question 2 without extremes values",
    col = c("#ff0000", "#ffa700", "#fff400", "#a3ff00", "#2cba00"),
    labels = paste0(names(table(data$answer_2)), ": ", (table(data$answer_2))))

legend("topright",
       legend = names((table(data$answer_2))),
       fill = c("#ff0000", "#ffa700", "#fff400", "#a3ff00", "#2cba00"),
       cex = 0.8,
       title = "Answers")

correlation <- cor(data$answer_1, data$answer_2)
print(paste('In the new dataset, the correlation is ', correlation))

plot <- ggplot(data, aes(x = answer_1, fill = as.factor(answer_2))) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("#ff0000", "#ffa700", "#fff400", "#a3ff00", "#2cba00")) + 
  labs(fill = "answer_2") +
  xlab("Time spended watching video (in min)") +
  ggtitle("Density of the time spended watching video per look at themselves 
          without the extremes values")

plot
```


Without the extreme values, the correlation drastically drops and is even negative that mean the more people watch video the better they feel with it.
In this region people's look on themselves is independent to the time they spend watching video.

In conclusion we can say that **we reject our hypothesis** but our idea seems valid outside of extreme values.
We also have to stress out the fact that this survey have been done on few people only. 


# Conclusion 
