---
title: "Assignment 2: Survey developpment"
subtitle: "105.708 Data Acquisition and Survey Methods"
author: "Group 3: Gjorgieva Aleksandra(), de Lambertye Grégoire(12202211),	Loos Annika Katharina()"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
suppressMessages(library(dplyr))
suppressMessages(library('xml2'))
suppressMessages(library(rvest))
suppressMessages(library(tidyverse))
suppressMessages(library(httr))
suppressMessages(library(janitor))
suppressMessages(library(lubridate))
```

# Introducction 

## topic

blabla 

## Hypothesis 

blabla 

## question 

blaba 

# Data exploration 

```{r}
file_path <- "./data/group_3.csv"

rawData <- read.csv(file_path, sep=";")
# rename the column in a english friendly format 
colnames(rawData)[4] <- "answer_1" 
colnames(rawData)[5] <- "answer_2" 
colnames(rawData)[6] <- "answer_3"

print(head(rawData))
print(paste("The data set dimensions are ", dim(rawData)[1], " x ", dim(rawData)[2]))
```

## Preprocessing 

The colummns Gender and Age look nice and don't requier preprocessing.  

## Academic programm

```{r}
print(unique(rawData[3]))
```
As we see the format differs for the academic program answer. Where we have missing information we associate them by default to Data Science / MSc / TU Wien. To say we change "Data Science", "MSc Data Science", "MSc", "Data Science Msc", "	Data Science MSc." to "Data Science / MSc / TU Wien". 

```{r}
row_index <- which(rawData$Academic.Program %in% c("Data Science", 
                                                   "Data Science / MSc / TU Wien", 
                                                   "MSc Data Science", 
                                                   "Data Science / MSc / TU WIen",
                                                   "MSc", 
                                                   "Data Science Msc", 
                                                   "Data Science MSc."))

rawData[row_index, "Academic.Program"] <- "Data Science / MSc / TU Wien"
```


```{r}

print(unique(rawData[3]))
```

```{r}
rawData$answer_2 <- str_sub(rawData$answer_2, end = 2)
rawData$answer_2 <- as.numeric(rawData$answer_2)
```


```{r}
for (i in 1:length(rawData$answer_1)){
  if(rawData$answer_1[i] <= 5){
    rawData$answer_1[i] <- rawData$answer_1[i] * 60
  }
}
```



```{r}
head(rawData)
```
 

# Analysis 

## hypothesis 1

## hypothesis 2

## hypothesis 3


# Conclusion 

